Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys

### 2023-07-15 analysis/analysis.qmd
confidence intervals for log odds in table 6

dframe %>% 
  dplyr::select(level, task, chart, estimate, std.error, letters) %>%
  mutate(
    task = ifelse(task=="ab", "Unaligned", "Aligned")
  ) %>%
  group_by(task) %>%
  mutate(
    estimate = exp(estimate),
    std.error = exp(std.error)
  ) %>%
  tidyr::pivot_wider(
        id_cols = c(task, chart),
        names_from = level,
        values_from = c(estimate, std.error, letters)
      ) %>%
  gt() %>%
  tab_header(title = "Log odds (SD) of accuracy by task and chart type") %>%
  fmt_number(
    everything(),
    decimals=2
  ) %>%
  cols_merge(
    columns = c("estimate_correct | same or wrong", "std.error_correct | same or wrong",
                "letters_correct | same or wrong"),
    pattern = "<<{1}>><< ({2})>><< {3}>>"
  ) %>%
  cols_merge(
    columns = c("estimate_correct or same | wrong", 
                "std.error_correct or same | wrong",
                "letters_correct or same | wrong"),
    pattern = "<<{1}>><< ({2})>><< {3}>>"
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  cols_label(
    .list = c(
      "chart" = "",
      "estimate_correct | same or wrong" = "correct | same or wrong",
      "estimate_correct or same | wrong" = "correct or same | wrong"
    )
  )
```

>>>>

dframe %>% 
  dplyr::select(level, task, chart, estimate, std.error, letters) %>%
  mutate(
    task = ifelse(task=="ab", "Unaligned", "Aligned")
  ) %>%
  group_by(task) %>%
  mutate(
    ci_low = exp(estimate-1.96*std.error),
    ci_high = exp(estimate+1.96*std.error),
    estimate = exp(estimate)
  ) %>%
  tidyr::pivot_wider(
        id_cols = c(task, chart),
        names_from = level,
        values_from = c(estimate, ci_low, ci_high, letters)
      ) %>%
  gt() %>%
  tab_header(title = "Log odds of accuracy by task and chart type") %>%
  fmt_number(
    everything(),
    decimals=2
  ) %>%
  cols_merge(
    columns = c("estimate_correct | same or wrong", "ci_low_correct | same or wrong",
                "ci_high_correct | same or wrong", "letters_correct | same or wrong"),
    pattern = "<<{1}>><< [{2}, {3}]>><< {4}>>"
  ) %>%
  cols_merge(
    columns = c("estimate_correct or same | wrong", "ci_low_correct or same | wrong",
                "ci_high_correct or same | wrong", "letters_correct or same | wrong"),
    pattern = "<<{1}>><< [{2}, {3}]>><< {4}>>"
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  cols_label(
    .list = c(
      "chart" = "",
      "estimate_correct | same or wrong" = "correct | same or wrong",
      "estimate_correct or same | wrong" = "correct or same | wrong"
    )
  )
```
